---
title: "Global Economic Indicators — Analytical Report"
author: "Boyinapalli Phani Shankar"
date: "`r Sys.Date()`"
output:
  html_document:
    theme:        flatly
    highlight:    tango
    toc:          true
    toc_float:    true
    number_sections: false
    df_print:     paged
    fig_width:    9
    fig_height:   5
params:
  countries:
    label:   "Countries"
    value:   !r c("India", "United States", "China", "Germany", "Brazil")
  start_year:
    label:   "Start Year"
    value:   2005
  end_year:
    label:   "End Year"
    value:   2023
  indicator:
    label:   "Indicator"
    value:   "GDP Growth (%)"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)

library(dplyr)
library(ggplot2)
library(plotly)
library(wbstats)
library(tidyr)
library(knitr)
library(kableExtra)

source("R/data_helpers.R")
source("R/plot_helpers.R")
```

```{r load-data}
wb_df <- fetch_wb_data(
  start_year = params$start_year,
  end_year   = params$end_year
)

df_filtered <- filter_data(
  df         = wb_df,
  countries  = params$countries,
  year_range = c(params$start_year, params$end_year),
  indicator  = params$indicator
)
```

---

## Overview

This report analyses **`r params$indicator`** for
**`r length(params$countries)` countries** over the period
**`r params$start_year`–`r params$end_year`**.

Countries covered: *`r paste(params$countries, collapse = ", ")`*

Data source: [World Bank Open Data](https://data.worldbank.org), retrieved
via the `wbstats` R package on `r Sys.Date()`.

---

## Trend Analysis

```{r trend-chart, fig.cap="Annual trend — hover to explore values."}
make_line_chart(df_filtered, params$indicator)
```

---

## Latest Snapshot

```{r bar-chart, fig.cap="Most recent available value per country."}
make_bar_chart(df_filtered, params$indicator)
```

---

## Summary Statistics

```{r summary-table}
tbl <- compute_summary(df_filtered)

tbl %>%
  kableExtra::kbl(
    caption = paste("Summary statistics —", params$indicator,
                    paste0("(", params$start_year, "–", params$end_year, ")")),
    align   = c("l", "r", "r", "r", "r")
  ) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width        = FALSE,
    position          = "left",
    font_size         = 13
  ) %>%
  kableExtra::column_spec(1, bold = TRUE)
```

---

## Key Findings

```{r findings}
highest <- tbl %>% dplyr::slice_max(Mean, n = 1)
lowest  <- tbl %>% dplyr::slice_min(Mean, n = 1)
```

- **Highest average `r params$indicator`:**
  `r highest$Country` at `r highest$Mean`%
- **Lowest average `r params$indicator`:**
  `r lowest$Country` at `r lowest$Mean`%
- **Total observations in dataset:** `r format(nrow(df_filtered), big.mark = ",")`

---

## How to Reproduce

To regenerate this report with different parameters, run the
following in RStudio:

```r
rmarkdown::render(
  "report.Rmd",
  params = list(
    countries  = c("India", "United States", "China"),
    start_year = 2010,
    end_year   = 2023,
    indicator  = "Inflation (%)"
  )
)
```

---

*Report generated by the Global Economic Indicators Shiny Dashboard
using R `r R.version.string`.*
